---
title: "Caregiver burden data preparation"
author: "Hans, Jenny, and Derek"
date: "May 14, 2017"
output: html_document
---

```{r setup, include=FALSE}
require(ExPosition)
require(knitr)
knitr::opts_chunk$set(echo = TRUE)

rinline <- function(code) {
  sprintf('``` %s ```', code)
}


```


# Overview

Our analyses focus on caregiver burden as the *outcome* from a variety of predictors, such as demographics, disorder type, cognitive function, and neuropsychogical profiles. 

# Load data and construct data set

The observations we work with require (1) at least summary scores from Zarit's (caregiver) burden interview (ZBI; CITE) and (2) must not classify as normal or missing in final diagnosis (FINDX). Conditional to the ZBI and FINDX, we include participants who qualify as:

* Dementia (community and institution; cgcc==1 | cgcc==3),
* Alzheimer's (adcc==1),
* Parkinson's disease (parkin==1), and
* Stroke (prstroke==1).

Not included for now (because there are so few amongst this set):

* Amyotrophic lateral sclerosis (als==1),
* Epilepsy (epilepsy==1), and
* Multiple sclerosis (ms==1).

Other conditions to consider later (as pseudo-controls): 

* Depression (depressn==1), 
* Learning Disability (learning==1), 
* Psychiatric Illness (psychiat==1), and/or 
* Migraines (migraine==1).


The following lines of code will read in the data and include only the subjects outlined in the above conditions.
```{r load data and cases, tidy=TRUE, tidy.opts=list(width.cutoff=55)}
  ## data exist one directory above and in a separate folder 
  ### (in part to avoid committing it to Github for now!)
CSHA.1991.full <- read.csv("../IPN2017_Case_Comp/Dataset.csv")

  ## Conditionals to extract specific participants
  ### start with primary outcome of interest: caregiver burden
CSHA.1991.zarit <- CSHA.1991.full[CSHA.1991.full$zarscore < 99,]
dim(CSHA.1991.zarit)

  ### Now get all data for above conditions
  conditions.of.interest <- c( 
      (CSHA.1991.zarit$cgcc==1 | 
      CSHA.1991.zarit$cgcc==3 |
      CSHA.1991.zarit$adcc==1 |
      CSHA.1991.zarit$parkin==1 |
      CSHA.1991.zarit$prstroke==1) &
      (CSHA.1991.zarit$finaldx !=0 & CSHA.1991.zarit$finaldx !=9)
    )
CSHA.1991.zarit_disorders <- CSHA.1991.zarit[conditions.of.interest,]  
dim(CSHA.1991.zarit_disorders)
```

We now have a subset of observations we should make a pseudo-design matrix of the conditionals above. We want to denote which of the aforementioned categories each individual belongs to:

```{r design matrix, tidy=TRUE, tidy.opts=list(width.cutoff=55)}
  cols.for.design <- c("CASEID","cgcc","adcc","parkin","prstroke","finaldx")
  CSHA.1991.zarit_disorders_design <- CSHA.1991.zarit_disorders[,cols.for.design]
  
  dim(CSHA.1991.zarit_disorders_design)
  head(CSHA.1991.zarit_disorders_design)
  
```

We can recode some of the values in these columns to something more sensible with a design matrix. The code below to perform the recoding is hidden from the output.


```{r sensible design, tidy=TRUE, tidy.opts=list(width.cutoff=55), include=FALSE}

  ##recode cgcc
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("0","N/A",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)

  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("1","COMM.CASE",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("2","COMM.CON",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("3","INS.CASE",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)  
  
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("4","INS.CON",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)  
  
  ##recode adcc.
  CSHA.1991.zarit_disorders_design$adcc <-
    gsub("0","N/A",CSHA.1991.zarit_disorders_design$adcc,fixed=T)

  CSHA.1991.zarit_disorders_design$adcc <-
    gsub("1","CASE",CSHA.1991.zarit_disorders_design$adcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$adcc <-
    gsub("2","CON",CSHA.1991.zarit_disorders_design$adcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$adcc <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$adcc,fixed=T)

  ##recode parkin
  CSHA.1991.zarit_disorders_design$parkin <- 
    gsub("1","YES",CSHA.1991.zarit_disorders_design$parkin,fixed=T)
  
  CSHA.1991.zarit_disorders_design$parkin <-
    gsub("2","NO",CSHA.1991.zarit_disorders_design$parkin,fixed=T)
  
  CSHA.1991.zarit_disorders_design$parkin <-
    gsub("8","DNK",CSHA.1991.zarit_disorders_design$parkin,fixed=T)

  CSHA.1991.zarit_disorders_design$parkin <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$parkin,fixed=T)  
  
  ##recode prstroke
  CSHA.1991.zarit_disorders_design$prstroke <- 
    gsub("1","YES",CSHA.1991.zarit_disorders_design$prstroke,fixed=T)
  
  CSHA.1991.zarit_disorders_design$prstroke <-
    gsub("2","NO",CSHA.1991.zarit_disorders_design$prstroke,fixed=T)
  
  CSHA.1991.zarit_disorders_design$prstroke <-
    gsub("8","DNK",CSHA.1991.zarit_disorders_design$prstroke,fixed=T)

  CSHA.1991.zarit_disorders_design$prstroke <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$prstroke,fixed=T)
  
 ##recode finaldx
  CSHA.1991.zarit_disorders_design$finaldx <-
    gsub("0","NORMAL",CSHA.1991.zarit_disorders_design$finaldx,fixed=T)

  CSHA.1991.zarit_disorders_design$finaldx <-
    gsub("1","COGLOSS",CSHA.1991.zarit_disorders_design$finaldx,fixed=T)

  CSHA.1991.zarit_disorders_design$finaldx <-
    gsub("2","PROB.ALZ",CSHA.1991.zarit_disorders_design$finaldx,fixed=T)

  CSHA.1991.zarit_disorders_design$finaldx <-
    gsub("3","POSS.ALZ",CSHA.1991.zarit_disorders_design$finaldx,fixed=T)

  CSHA.1991.zarit_disorders_design$finaldx <-
    gsub("4","VDEM",CSHA.1991.zarit_disorders_design$finaldx,fixed=T)

  CSHA.1991.zarit_disorders_design$finaldx <-
    gsub("5","OTHER.DEM",CSHA.1991.zarit_disorders_design$finaldx,fixed=T)

  CSHA.1991.zarit_disorders_design$finaldx <-
    gsub("6","UNCLASS.DEM",CSHA.1991.zarit_disorders_design$finaldx,fixed=T)

  CSHA.1991.zarit_disorders_design$finaldx <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$finaldx,fixed=T)

  
  colnames(CSHA.1991.zarit_disorders_design) <- c("CASEID","DEMENTIA","ALZ","PD","STROKE","FIN.DX")  
  rownames(CSHA.1991.zarit_disorders_design) <- CSHA.1991.zarit_disorders_design$CASEID
  
  CSHA.design <- makeNominalData(CSHA.1991.zarit_disorders_design[,c("DEMENTIA","ALZ","PD","STROKE","FIN.DX")])
  
  
```

```{r show_design}
  head(CSHA.1991.zarit_disorders_design)
  head(CSHA.design)
  
  colSums(CSHA.design)
```

We now have a pseudo-design matrix to identify observation disorder classifications. Now we want to extract just particular sets of columns as predictors and outcomes from our subset. 


```{r predsouts, tidy=TRUE, tidy.opts=list(width.cutoff=55)}

  ## predictors
  ### demographics
  demographics <- c("studysex","agestrat","studyage","clinage","studyed","eduyear","edulevel","region","race","ethnic1","ethnic2","wbocc","working","institut")
  ### caregiver demographics
  cg.demographics <- c("relat","cgsex","cgage","cgeth1","cgeth2","cgedyrs","cgedlev")
  ### cognition
  cognition <- c("langabil","mmms","score3ms")
  ### behavioral disturbance
  beh.disturb <- c("apathy","wander","violenc","disinhi","otherbe")
  
  
  ### full neuropsych
    ### neuropsych batteries
  neuropsych <- c("neurdone","languagn","doi","occup","materlan","difficul","othrcomn","psyid","clinic","training","experien","coopern","facility","fatigabi","inattn","affectn","articul","tension","appearn","reaction","effort","express","memoryn","restless","insight","gaitn","agitat","persever","impulsiv","socialn","tangent","comprehe","confusi","latency","rulev","tolerate","visionn","hearingn","physical","gaitdiso","tremdiso","dyskdiso","psycdiso","slowdiso","hearaid","glasses","wheel","wechsler","buschfr1","buschcr1","buschtr1","buschfr2","buschcr2","buschtr2","buschfr3","buschcr3","buschtr3","buschfr","buschcr","buschtr","delaytim","reya1","reya2","reya3","reya4","reya5","reya6","reyb1","trueposi","truenega","correct","benmirro","digitspa","lag1","lag2","waisimil","waisjudg","tokentes","verbal","animal","buschke","visualn","tokencol","waisbloc","digit","popsize","nshorter","nlongter","nverbal","njudgeme","naphasia","napraxia","nagnosia","nconstru","ndisturb","delirium","majordep","diagdeme","profile","corticr","corticl","subcort","cnocoglo","ccogloss","cad","cvasdem","cother","cunclass","daily","ndiag","severity","shrtlosn","longlosn","clanguag","cdofint","cintid","c235","c236","c236a","c237","c238","c239","c240","c241","c242","c243","c244","c245","c246","c247","c248","c249","c250","c251","c252","c253","c253am","c253ay","c253bm","c253by","c254","c255","c256","c257","c258","c259","c260","c261","c262","c263","c264","c265","c266","c267","c268","c269","c270","c271","c272","c273","c274","c275","c276","c277","c278","c279","c280","c281","c282","c283","c284","c285","c286","c286a","c287","c287a","c288","c289","c290","c291","c292","c293","c294","c295","c296","c297","c298","c299","c300","c301","c302","c303","c304","c305","c306","c307","c308","c309","c310","c311","c312","c313","c314","c315","c316","c317","c318","c319","c320","c321","c322","c323","c324","c325","c326","c327","c328","c329","c330","c331","c332","c333")
  
  #### neuropsych: behavioral ratings
  np.beh_rate <- c("coopern","facility","fatigabi","inattn","affectn","articul","tension","appearn","reaction","effort","express","memoryn","restless","insight","gaitn","agitat","persever","impulsiv","socialn","tangent","comprehe","confusi","latency","rulev","tolerate","visionn","hearingn","physical","hearaid","glasses","wheel")
  #### neuropsych: movement disorders
  np.move_disorder <- c("gaitdiso","tremdiso","dyskdiso","psycdiso","slowdiso")
  #### neuropsych: memory, fluency, etc...
  np.battery <- c("wechsler","buschfr1","buschcr1","buschtr1","buschfr2","buschcr2","buschtr2","buschfr3","buschcr3","buschtr3","buschfr","buschcr","buschtr","delaytim","reya1","reya2","reya3","reya4","reya5","reya6","reyb1","trueposi","truenega","correct","benmirro","digitspa","lag1","lag2","waisimil","waisjudg","tokentes","verbal","animal","buschke","visualn","tokencol","waisbloc","digit")
  #### neuropsych: impairments & diagnoses
  np.impair_diagnoses <- c("nshorter","nlongter","nverbal","njudgeme","naphasia","napraxia","nagnosia","nconstru","ndisturb","delirium","majordep","diagdeme","profile","corticr","corticl","subcort","cnocoglo","ccogloss","cad","cvasdem","cother","cunclass","daily","ndiag","severity","shrtlosn","longlosn")
  #### neuropsych: personality  
  np.personality <- c("c238","c239","c240","c241","c242","c243","c244","c245","c246")
  #### neuropsych: memory
  np.memory <- c("c247","c248","c249","c250","c251","c252","c253","c253am","c253ay")
  #### neuropsych: general function
  np.gen_func <- c("c253bm","c253by","c254","c255","c256","c257","c258","c259","c260","c261","c262")
  #### neuropsych: every day activities
  np.everyday <- c("c263","c264","c265","c266","c267","c268","c269")
  #### neuropsych: delerium
  np.delerium <- c("c270","c271","c272","c273","c274")
  #### neuropsych: depression
  np.depress <- c("c275","c276","c277","c278","c279")
  #### neuropsych: sleep
  np.sleep <- c("c280","c281","c282","c283","c284","c285")
  #### neuropsych: paranoia
  np.paranoia <- c("c286","c286a","c287","c287a")
  #### neuropsych: cardiovascular
  np.cv <- c("c288","c289","c290","c291")
  #### neuropsych: summary
  np.gen_sum <- c("c292","c293","c294")
  #### neuropsych: past medical history
  np.history <- c("c295","c296","c297","c298","c299","c300","c301","c302","c303","c304","c305","c306","c307","c308","c309","c310")
  
  
  
  ## variables that exist somewhere between predictors and additional variables of interest
  ### dementia
  dementia <- c("shorterm","longterm","abstract","judgemen","aphasia","apraxia","agnosia","construc","change","work","social","relation")
  ### alzheimer's
  alz <- c("addement","adcognit","adworsen","adconsci","onsetage","absence")
  
  
  ## possible predictors/mediators/variables of interest or confounds.
  ### Family history
  famhistory <- c("twin","samesex","identic","familyhs","alz1","alz2","alz3","sen1","sen2","sen3","par1","par2","par3")
  ### languages spoken
  languages <- c("english","french","italian","german","spanish","iceland","ukrain","chinese","japanese","danish","arabic","urdu","otherlan")
  ### health issues
  health.drugs <- c("thycond","attack","oheart","leukemia","cancer","proxdiab","hbpyr","drug","height","sweight")
  ### regular substance use -- COMBINE SMOKING & DRINKING & CAFFEIENE/SUGAR
  substances <- c("coffee","tea","drinks","smoke","pipe","cigars","beer","wine","spirits")
  ### head injuries
  head.inj <- c("consloss","consage")
  ### depression
  depress <- c("sad","interest","appetite","lossweig","asleep","awaken","allday","tiredall","move","worthles","suicide","most","impress")

  
  ## outcomes
  ### caregiver questions/situation
  cg.unpaid <- c("askhelp","notime","feelstre","feelemba","feelangr","affects","afraid","dependen","strained","suffered","privacy","soclife","friends","expect","expenses","unable","lostctrl","leave","uncertai","doing","better","burdened","zarscore","health1", "health2")
  ### caregiver "felt"
  cg.felt <- c("bother","poorapp","shake","good","mind","depressd","eveffort","hopeful","failure","fearful","restls","happy","talkless","lonely","unfriend","enjoylif","cryspell","feltsad","dislike","getgoing","cesscore")
  
  
  targeted.predictors <- CSHA.1991.zarit_disorders[,c("CASEID", demographics, cg.demographics, cognition, beh.disturb, np.battery)]
  
  full.predictors <- CSHA.1991.zarit_disorders[,c("CASEID",demographics,famhistory,cg.demographics,languages,health.drugs,substances,head.inj,cognition,beh.disturb,depress,dementia,alz,neuropsych)]  
  
  outcomes <- CSHA.1991.zarit_disorders[,c("CASEID",cg.unpaid,cg.felt)]
  
  dim(targeted.predictors)
  dim(full.predictors)
  dim(outcomes)
  
  
```


For our project we should begin with just the two sets of variables identified as `target.predictors` and `outcomes`. At this point we have some re-coding to do to convert missing and NA codes, and to convert YES/NO responses or scales to a more coherent format.

```{r recoding missingness, tidy=TRUE, tidy.opts=list(width.cutoff=55)}
## Recoding Missing Values with NA
## Predictor Variables (full set)

## Variables with missing == 7 | 8 | 9
vars.missing.x<- c("region","race","wbocc","working","institut","cgsex","langabil","apathy","wander","violenc","disinhi","otherbe","neurdone","languagn","occup","difficul","othrcomn","clinic","training","experien","coopern","facility","fatigabi","inattn","affectn","articul","tension","appearn","reaction","effort","express","memoryn","restless","insight","gaitn","agitat","persever","impulsiv","socialn","tangent","comprehe","confusi","latency","rulev","tolerate","visionn","hearingn","physical","gaitdiso","tremdiso","dyskdiso","psycdiso","slowdiso","hearaid","glasses","wheel","wechsler","tokencol","popsize","nshorter","nlongter","nverbal","njudgeme","naphasia","napraxia","nagnosia","nconstru","ndisturb","delirium","majordep","diagdeme","profile","corticr","corticl","subcort","daily","severity","shrtlosn","longlosn","clanguag","c235","c236a","c238","c239","c240","c241","c242","c243","c244","c246","c247","c248","c249","c250","c251","c253","c254","c255","c256","c257","c258","c259","c261","c262","c263","c264","c265","c266","c267","c269","c270","c271","c272","c273","c275","c276","c277","c279","c280","c281","c282","c283","c285","c286","c287","c288","c289","c290","c292","c295","c296","c297","c298","c299","c300","c301","c302","c303","c304","c305","c306","c307","c308","c309","c310",dementia,alz,"twin","samesex","identic","familyhs",languages,"thycond","attack","oheart","leukemia","cancer","proxdiab","drug",substances,"consloss",depress)

 ## Variables with missing == 66 | 77 | 88 | 98 | 99
vars.missing.xx<-c("studyed","eduyear","edulevel","ethnic1","ethnic2","relat","cgeth1","cgeth2","cgedyrs","cgedlev","materlan","buschfr1","buschcr1","buschtr1","buschfr2","buschcr2","buschtr2","buschfr3","buschcr3","buschtr3","buschfr","buschcr","buschtr","delaytim","reya1","reya2","reya3","reya4","reya5","reya6","reyb1","trueposi","truenega","correct","benmirro","digitspa","lag1","lag2","waisimil","waisjudg","tokentes","verbal","animal","buschke","visualn","waisbloc","cnocoglo","ccogloss","cad","cvasdem","cother","cunclass","c253am","c253bm","c311","c312","c313","c314","c316","c318","c319","c320","c321","c322","c323","c324","c325","c326","c327","c328","c329","c330","c331","c332","c333","alz1","alz2","alz3","sen1","sen2","sen3","par1","par2","par3")

## Variables with missing == 777 | 888 | 996| 997| 998 | 999 <- some of these varaibles have legit scores of 666 hence the separate coding
vars.missing.xxx<-c("cgage","mmms","score3ms","psyid","ndiag","cintid","digit","c245","c252","c253ay","c253by","c260","c268", "c274","c278","c284","c286a","c287a", "c291","c293","c294","c315","c317","height","consage")

## Variables with missing = 999999
vars.missing.xxxxxx<-c("doi","cdofint")

## Variables with 0 coded as "skipped" or "miscoded" or "not applicable"
vars.skipped.0<-c("ethnic2","cgeth2","insight","napraxia","ndisturb","delirium","majordep","c315","c316","c317","samesex","identic","sen1","consloss","consage")

## Variables with 6 coded as missing (visual/hearing/motor/blind)
vars.missing.6<-c(beh.disturb,"tokencol","nshorter","nverbal","naphasia","napraxia","nagnosia","nconstru","ndisturb","severity","shrtlosn","longlosn","impress")
vars.missing.5<-c(beh.disturb,"impress")
vars.missing.4<-c(beh.disturb)
## Variables with 666 coded as missing(visual/hearing)
vars.missing.666<-c("digit","c253ay","c253by")

## random variables with very special coding
vars.missing.9.only<-c("c236","c237")  ## 7 & 8 are actual values

## vars with missing code above 80 (decimal coding)
vars.missing80plus<-c("hbpyr","sweight")

############
full.predictors.NAs<-full.predictors

full.predictors.NAs[,vars.missing.x]<-apply(full.predictors.NAs[,vars.missing.x],2,function(x) {x[(x==7 | x==8 | x==9)] <- NA; x})
full.predictors.NAs[,vars.missing.xx]<-apply(full.predictors.NAs[,vars.missing.xx],2,function(x) {x[(x==77 | x==88 | x==99 | x==66 | x == 98)] <- NA; x})
full.predictors.NAs[,vars.missing.xxx]<-apply(full.predictors.NAs[,vars.missing.xxx],2,function(x) {x[(x==777 | x==888 | x==999 | x==996 | x == 997 | x == 998)] <- NA; x})
full.predictors.NAs[,vars.missing.xxxxxx]<-apply(full.predictors.NAs[,vars.missing.xxxxxx],2,function(x) {x[(x==999999)] <- NA; x})
full.predictors.NAs[,vars.skipped.0]<-apply(full.predictors.NAs[,vars.skipped.0],2,function(x) {x[(x==0)] <- NA; x})
full.predictors.NAs[,vars.missing.6]<-apply(full.predictors.NAs[,vars.missing.6],2,function(x) {x[(x==6)] <- NA; x})
full.predictors.NAs[,vars.missing.5]<-apply(full.predictors.NAs[,vars.missing.5],2,function(x) {x[(x==5)] <- NA; x})
full.predictors.NAs[,vars.missing.4]<-apply(full.predictors.NAs[,vars.missing.4],2,function(x) {x[(x==4)] <- NA; x})
full.predictors.NAs[,vars.missing.666]<-apply(full.predictors.NAs[,vars.missing.666],2,function(x) {x[(x==666)] <- NA; x})
full.predictors.NAs[,vars.missing.9.only]<-apply(full.predictors.NAs[,vars.missing.9.only],2,function(x) {x[(x==9)] <- NA; x})
full.predictors.NAs[,vars.missing80plus]<-apply(full.predictors.NAs[,vars.missing80plus],2,function(x) {x[(x>80)] <- NA; x})

targeted.predictors.NAs <- full.predictors.NAs[,c("CASEID", demographics, cg.demographics, cognition, beh.disturb, np.battery)]
#summary(targeted.predictors.NAs)  
summary(full.predictors.NAs)  

### Recoding Outcome variables

## Variables with missing == 7 | 8 | 9
out.missing.x<-c("askhelp","notime","feelstre","feelemba","feelangr","affects","afraid","dependen","strained","suffered","privacy","soclife","friends","expect","expenses","unable","lostctrl","leave","uncertai","doing","better","burdened","bother","poorapp","shake","good","mind","depressd","eveffort","hopeful","failure","fearful","restls","happy","talkless","lonely","unfriend","enjoylif","cryspell","feltsad","dislike","getgoing","health1", "health2")

## Variables with missing == 99
out.missing.xx<-c("zarscore","cesscore")

###
outcomes.NAs<-outcomes

outcomes.NAs[,out.missing.x]<-apply(outcomes.NAs[,out.missing.x],2,function(x) {x[(x==7 | x==8 | x==9)] <- NA; x})
outcomes.NAs[,out.missing.xx]<-apply(outcomes.NAs[,out.missing.xx],2,function(x) {x[(x==99)] <- NA; x})

summary(outcomes.NAs)
```

Recoding notes and things to be mindful of:

* In general, 7 = refused; 8 = do not know; 9 = missing (all coded as NA in final dataset)
* For neuropsych, 66 = visual/hearing impairment
* all beh.disturb vars have additional coding scheme: not relavent = 4; dnk = 5; could not answer = 6; missing = 9
* coding for score3ms is slightly different for 777 and 888 (see codebook); but coded as NAs for now








