---
title: "Caregiver burden data preparation"
author: "Hans, Jenny, and Derek"
date: "May 14, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
require(ExPosition)
require(knitr)
knitr::opts_chunk$set(echo = TRUE)

rinline <- function(code) {
  sprintf('``` %s ```', code)
}


```


# Overview

Our analyses focus on caregiver burden as the *outcome* from a variety of predictors, such as demographics, disorder type, cognitive function, and neuropsychogical profiles. 

# Load data and construct data set

The observations we work with require at least summary scores from Zarit's (caregiver) burden interview (ZBI; CITE). Conditional to the ZBI, we include participants who classify as:

* Dementia (community and institution),
* Alzheimer's,
* Parkinson's disease,
* Amyotrophic lateral sclerosis,
* Stroke,
* Epilepsy, and
* Multiple sclerosis.

Other conditions to consider (perhaps for later): Depression (depressn==1), Learning Disability (learning==1), Psychiatric Illness (psychiat==1), or Migraines (migraine==1).


The following lines of code will read in the data and include only the subjects outlined in the above conditions.
```{r load data and cases, tidy=TRUE, tidy.opts=list(width.cutoff=55)}
  ## data exist one directory above and in a separate folder 
  ### (in part to avoid committing it to Github for now!)
CSHA.1991.full <- read.csv("../IPN2017_Case_Comp/Dataset.csv")

  ## Conditionals to extract specific participants
  ### start with primary outcome of interest: caregiver burden
CSHA.1991.zarit <- CSHA.1991.full[CSHA.1991.full$zarscore < 99,]
dim(CSHA.1991.zarit)

  ### Now get all data for above conditions
  conditions.of.interest <- (
      CSHA.1991.zarit$cgcc==1 |     # Dementia: COMMUNITY CASE
      CSHA.1991.zarit$cgcc==3 |     # Dementia: INSTITUTION CASE
      CSHA.1991.zarit$adcc==1 |     # Alzheimer's: YES
      CSHA.1991.zarit$parkin==1 |   # Parkinson's: YES
      CSHA.1991.zarit$prstroke==1 | # Stroke: YES
      CSHA.1991.zarit$als==1 |      # ALS: YES  
      CSHA.1991.zarit$epilepsy==1 | # Epilepsy: YES
      CSHA.1991.zarit$ms==1         # Multiple sclerosis: YES
    )
CSHA.1991.zarit_disorders <- CSHA.1991.zarit[conditions.of.interest,]  
dim(CSHA.1991.zarit_disorders)
```

We now have a subset of observations we should make a pseudo-design matrix of the conditionals above. We want to denote which of the aforementioned categories each individual belongs to:

```{r design matrix, tidy=TRUE, tidy.opts=list(width.cutoff=55)}
  cols.for.design <- c("cgcc","adcc","parkin","prstroke","als","epilepsy","ms")
  CSHA.1991.zarit_disorders_design <- CSHA.1991.zarit_disorders[,cols.for.design]
  
  dim(CSHA.1991.zarit_disorders_design)
  head(CSHA.1991.zarit_disorders_design)
  
```

We can recode some of the values in these columns to something more sensible with a design matrix. The code below is hidden from the output.

```{r what}
summary(as.factor(CSHA.1991.zarit_disorders_design$adcc))
```

```{r sensible design, tidy=TRUE, tidy.opts=list(width.cutoff=55), include=FALSE}

  ##recode cgcc
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("0","N/A",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)

  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("1","COMM.CASE",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("2","COMM.CON",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("3","INS.CASE",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)  
  
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("4","INS.CON",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$cgcc <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$cgcc,fixed=T)  
  
  ##recode adcc.
  CSHA.1991.zarit_disorders_design$adcc <-
    gsub("0","N/A",CSHA.1991.zarit_disorders_design$adcc,fixed=T)

  CSHA.1991.zarit_disorders_design$adcc <-
    gsub("1","CASE",CSHA.1991.zarit_disorders_design$adcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$adcc <-
    gsub("2","CON",CSHA.1991.zarit_disorders_design$adcc,fixed=T)
  
  CSHA.1991.zarit_disorders_design$adcc <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$adcc,fixed=T)

  ##recode parkin
  CSHA.1991.zarit_disorders_design$parkin <- 
    gsub("1","YES",CSHA.1991.zarit_disorders_design$parkin,fixed=T)
  
  CSHA.1991.zarit_disorders_design$parkin <-
    gsub("2","NO",CSHA.1991.zarit_disorders_design$parkin,fixed=T)
  
  CSHA.1991.zarit_disorders_design$parkin <-
    gsub("8","DNK",CSHA.1991.zarit_disorders_design$parkin,fixed=T)

  CSHA.1991.zarit_disorders_design$parkin <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$parkin,fixed=T)  
  
  ##recode prstroke
  CSHA.1991.zarit_disorders_design$prstroke <- 
    gsub("1","YES",CSHA.1991.zarit_disorders_design$prstroke,fixed=T)
  
  CSHA.1991.zarit_disorders_design$prstroke <-
    gsub("2","NO",CSHA.1991.zarit_disorders_design$prstroke,fixed=T)
  
  CSHA.1991.zarit_disorders_design$prstroke <-
    gsub("8","DNK",CSHA.1991.zarit_disorders_design$prstroke,fixed=T)

  CSHA.1991.zarit_disorders_design$prstroke <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$prstroke,fixed=T)
  
  ##recode als
  CSHA.1991.zarit_disorders_design$als <- 
    gsub("1","YES",CSHA.1991.zarit_disorders_design$als,fixed=T)
  
  CSHA.1991.zarit_disorders_design$als <-
    gsub("2","NO",CSHA.1991.zarit_disorders_design$als,fixed=T)
  
  CSHA.1991.zarit_disorders_design$als <-
    gsub("8","DNK",CSHA.1991.zarit_disorders_design$als,fixed=T)

  CSHA.1991.zarit_disorders_design$als <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$als,fixed=T)  
  
  ##recode epilepsy
  CSHA.1991.zarit_disorders_design$epilepsy <- 
    gsub("1","YES",CSHA.1991.zarit_disorders_design$epilepsy,fixed=T)
  
  CSHA.1991.zarit_disorders_design$epilepsy <-
    gsub("2","NO",CSHA.1991.zarit_disorders_design$epilepsy,fixed=T)
  
  CSHA.1991.zarit_disorders_design$epilepsy <-
    gsub("8","DNK",CSHA.1991.zarit_disorders_design$epilepsy,fixed=T)

  CSHA.1991.zarit_disorders_design$epilepsy <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$epilepsy,fixed=T)
  
  ##recode ms
  CSHA.1991.zarit_disorders_design$ms <- 
    gsub("1","YES",CSHA.1991.zarit_disorders_design$ms,fixed=T)
  
  CSHA.1991.zarit_disorders_design$ms <-
    gsub("2","NO",CSHA.1991.zarit_disorders_design$ms,fixed=T)
  
  CSHA.1991.zarit_disorders_design$ms <-
    gsub("8","DNK",CSHA.1991.zarit_disorders_design$ms,fixed=T)

  CSHA.1991.zarit_disorders_design$ms <-
    gsub("9","MISSING",CSHA.1991.zarit_disorders_design$ms,fixed=T)
  
  colnames(CSHA.1991.zarit_disorders_design) <- c("DEMENTIA","ALZ","PD","STROKE","ALS","EPI","MS")
  
  CSHA.design <- makeNominalData(CSHA.1991.zarit_disorders_design)
```

```{r show_design}
  head(CSHA.1991.zarit_disorders_design)
  head(CSHA.design)
  
  colSums(CSHA.design)
```